\textbf{Proof Reconstruction in Classical Propositional Logic}

### 2017-08-14 slides/Jonathan-Proof-Reconstruction.tex
[ slides ] fixed conjunct function.
[ paper ] adding ndeduction tree example.

% \setmonofont[ExternalLocation=fonts/
%   , BoldFont=SourceCodePro-Semibold.ttf
%   , BoldItalicFont=SourceCodePro-SemiboldIt.ttf
%   , ItalicFont=SourceCodePro-It.ttf
%   ]{SourceCodePro-Regular.ttf}

@@

\usepackage{minted}
\setminted[cagda]{
  bgcolor   = aliceblue
, fontsize  = \footnotesize
, frame     = none
% , framerule = 0.4pt
% , framesep  = 0pt
, style     = cagda
}

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}}
\subtitle{(work in progress)}
\date{May 11, 2017\\Updated: \today}
\author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
(joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Master in Applied Mathematics\\
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\begin{frame}[fragile, label=atp-conjunct-proof]{The \texttt{conjunct} function and its theorem, \texttt{atp-conjunct}}
\vfill
\begin{minted}{cagda}
conjunct : (φ ψ : Prop) → Prop
conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
... | _          | []        = φ
... | conj _ _   | pick  ∷ _ = φ
... | conj φ₁ _  | proj₁ ∷ _ = conjunct φ₁ ψ
... | conj _ φ₂  | proj₂ ∷ _ = conjunct φ₂ ψ
... | other .φ   | _         = φ

@@

\begin{frame}[fragile, label=verified-example]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof generated with \texttt{Athena}}
\vfill
\begin{minted}{cagda}
p, q, a, goal, subgoal₀, subgoal₁ : Prop

@@

proof₀ : Γ ⊢ subgoal₀
proof₀ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-canonicalize
          (atp-strip
            (assume {Γ = Γ} (atp-negate subgoal₀))))
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal₀)
              (assume {Γ = ∅} a)))))))
\end{minted}
\vfill
\end{frame}

\begin{frame}[fragile, label=verified-example-3]{Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
subgoal₁ : Prop
subgoal₁ = q ⇒ p

proof₁ : Γ ⊢ subgoal₁
proof₁ =
  (RAA
    (atp-canonicalize
      (atp-simplify
        (atp-conjunct (q)
          (atp-canonicalize
            (weaken (atp-negate subgoal₁)
              (assume {Γ = ∅} a))))
        (atp-simplify
          (atp-canonicalize
            (atp-strip
              (assume {Γ = Γ} (atp-negate subgoal₁))))
          (atp-conjunct (p)
            (atp-canonicalize
              (weaken (atp-negate subgoal₁)
                (assume {Γ = ∅} a))))))))
\end{minted}
\vfill
\end{frame}

>>>>

@@

,

@@

\title[Proof Reconstruction in Classical Propositional Logic]
  {\textbf{Proof Reconstruction in Classical Propositional Logic}}
\subtitle{(work in progress)}
\date{Agda Implementors’ Meeting XXV\\
Teknikparken, Chalmers, Gothenburg, Sweden\\
May 11 2017\\[2mm]
Updated: \today}
\author[Jonathan Prieto-Cubides]{Jonathan Prieto-Cubides\\
(joint work with Andr\'es Sicard-Ram\'irez)}
\institute{
Master in Applied Mathematics\\
Universidad EAFIT\\
Medell\'in, Colombia}
% --------------------------------------------------------------------------

@@

\begin{frame}[fragile, label=atp-conjunct-proof]{The \texttt{conjunct} function and its theorem, \texttt{atp-conjunct}}
\vfill
\begin{minted}{cagda}
conjunct : Prop → Prop → Prop
conjunct φ ψ with conj-view φ | conjunct-path φ ψ []
... | _          | []        = φ
... | conj _ _   | pick  ∷ _ = φ
... | conj φ₁ _  | proj₁ ∷ _ = conjunct φ₁ ψ
... | conj _ φ₂  | proj₂ ∷ _ = conjunct φ₂ ψ
... | other .φ   | _         = φ

@@

\begin{frame}[fragile, label=verified-example]{Problem $p ∧ q ⊢ q ∧ p$}{Proof generated with \texttt{Athena}}
\vfill
\begin{minted}{cagda}
p, q, a, goal, subgoal₀, subgoal₁ : Prop

@@

proof₀ : Γ ⊢ subgoal₀
proof₀ =
  (RAA
    (atp-simplify ⊥
      (assume {Γ = Γ}
        (¬ subgoal₀))
      (atp-conjunct q
        (atp-canonicalize (p ∧ q)
          (weaken (¬ subgoal₀)
            (assume {Γ = ∅} a))))))
\end{minted}
\vfill
\end{frame}

\begin{frame}[fragile, label=verified-example-3]
  {Problem $p ∧ q ⊢ q ∧ p$}{Reconstructed Proof}
\vfill
\begin{minted}{cagda}
subgoal₁ : Prop
subgoal₁ = q ⇒ p

proof₁ : Γ ⊢ subgoal₁
proof₁ =
  (RAA
    (atp-simplify ⊥
      (atp-conjunct q
        (atp-canonicalize (p ∧ q)
          (weaken (¬ subgoal₁)
            (assume {Γ = ∅} a))))
      (atp-simplify ⊥
        (atp-canonicalize ((¬ p) ∧ q)
          (assume {Γ = Γ}
            (¬ subgoal₁)))
        (atp-conjunct p
          (atp-canonicalize (p ∧ q)
            (weaken (¬ subgoal₁)
              (assume {Γ = ∅} a)))))))
\end{minted}
\vfill
\end{frame}
